Varying paths to building the social state in the progressive era

### 2023-11-03 t1_analysis.Rmd
add models

```{r}
### FIT PROBLEM WAS WITH EARLY YEARS NEAR ZERO AND LOW VARIANCE
model_dat <- dat %>% 
  filter(year>=1880) %>% 
  mutate(police_rate = (police + 1) / tot_pop * 1e5,
         socwork_rate = (socwork + 1) / tot_pop * 1e5,
         teacher_rate = (teachers + 1) / tot_pop * 1e5,
         child_inst_rate = (child_inst_poor_disabled + 0.1) / 
           children * 1e5,
         hsclaim_prop = hs_claims / tot_pop,
         year = scale(year))

@@

sc_gq<-brm(log(child_inst_rate) ~ 
              scale(hsclaim_prop) +
              year + 
              (1 + year|state),
            data = model_dat)
```

@@

exp(t1)
```

>>>>

```{r}
### FIT PROBLEM WAS WITH EARLY YEARS NEAR ZERO AND LOW VARIANCE
model_dat <- dat %>% 
  filter(year>=1880) %>% 
  mutate(police_rate = (police + 1) / tot_pop * 1e5,
         socwork_rate = (socwork + 1) / tot_pop * 1e5,
         teacher_rate = (teachers + 1) / tot_pop * 1e5,
         child_inst_rate = (child_inst_poor_disabled + 0.1) / 
           children * 1e5,
         prop_blk = (blk + 1) / tot_pop,
         hsclaim_prop = hs_claims / tot_pop,
         year = scale(year))

@@

sc_gq<-brm(log(child_inst_rate) ~ 
              scale(hsclaim_prop) +
              year + 
              (1 + year|state),
            data = model_dat)

jc_police<-lmer(log(police_rate) ~ 
              scale(prop_blk) +
              year + 
              (1 + year|state),
            data = model_dat,
            control=lmerControl(optimizer="nloptwrap",
                                optCtrl=list(maxfun=2e5)))

jc_teacher<-lmer(log(teacher_rate) ~ 
              scale(prop_blk) +
              year + 
              (1 + year|state),
            data = model_dat,
            control=lmerControl(optimizer="nloptwrap",
                                optCtrl=list(maxfun=2e5)))

jc_socwork<-lmer(log(socwork_rate) ~ 
              scale(prop_blk) +
              year + 
              (1 + year|state),
            data = model_dat,
            control=lmerControl(optimizer="nloptwrap",
                                optCtrl=list(maxfun=2e5)))

jc_gq<-lmer(log(child_inst_rate) ~ 
              scale(prop_blk) +
              year + 
              (1 + year|state),
            data = model_dat,
            control=lmerControl(optimizer="nloptwrap",
                                optCtrl=list(maxfun=2e5)))
```

@@

exp(t1)
